First and foremost, I am extremely grateful to my master dissertation supervisor Dr. Kamesh Subbarao for his invaluable guidance and support throughout the process of this dissertation development. I am thankful to him for his belief in me to pursue research on one of the emerging field deep learning of which I have never been introduced and for providing me a research assistant position at Aerospace System Laboratory (ASL). I am honored to have such a great opportunity to upgrade my technical skill simultaneously with performing experiments. 

I would like to express my gratitude to the members of my dissertation committee Dr. Animesh Chakravarthy and Dr. Alan Bowling for taking time out to provide their inputs to make this work possible. Additionally, I am thankful to the administrative staff in the Mechanical and Aerospace Engineering department for all guidance related to the documentation. I would also like to acknowledge the staff at the Office of International Education for their guidance related to maintaining my international student status throughout the development process of my dissertation and organizing the webinar of all aspects that the international students have to take care of. 

Secondly, I am thankful to my parents who financially and morally supported me throughout my educational life and providing me the freedom to pursue study in the field of my interest. I am blessed to be the child of one of the best parents in this world. Moreover, I would like to thank all my friends for their generous help wherever required and for helping in making my baby steps in at the starting of the research work. 

Finally, I would like to thank Professor Andrew Ng for launching a great Massive Open Online Courses (MOOCs) on Coursera where I have been first introduced to deep learning. Additionally,  I am thankful to Mathworks Inc. and its technical support team for help me debugging the program and introducing a tool-set related to the work I was doing.   
    